---
title: "Prediction of microlithiasis"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    theme: cosmo
    orientation: rows
---
<style>                     
.navbar {
  background-color:#003D79;
  border-color:white;
}
.navbar-brand {
color:white!important;
}
</style>   

<style type="text/css">

.chart-title {  /* chart_title  */
   font-size: 15px

</style>

```{r setup, include=FALSE}
# load required packages
requirePackages <- c("dplyr", "tidyr", "ggplot2", "ggbeeswarm", "h2o", "lime", "flexdashboard", "shiny", "here")
loadPackages <- function(x) {
  for(i in 1:length(x)){
    if((x[i] %in% .packages(all.available=TRUE)) == TRUE) {
      eval(parse(text=paste("require(", x[i], ")", sep="")))
    } else {
      eval(parse(text=paste("install.packages('", x[i], "')", sep="")))
    }
  }
}
# load packages --------
loadPackages(requirePackages)

# set working directory
here::here()

# basic theme  -----------
ggplot_theme <- theme_bw() +
  theme(axis.line = element_line(size=0.75), axis.text = element_text(size=11, face="bold", colour = "black"), 
        axis.title = element_text(size=12, face="bold"),
        plot.title = element_text(size = 30, face = "bold")) +
  theme(legend.position = "bottom")

# initiate h2o -----------
# Sys.setenv(JAVA_HOME = "/dss/dsshome1/lxc00/ru64waf2/bin/jdk-13.0.2")
h2o.init()
h2o.no_progress()
h2o.removeAll()
# load model --------------
model <-
  h2o.loadModel("GBM_grid__1_AutoML_20220706_153327_model_2")
# model class -------------
class(model)
# variable importance table -------------
loess.Table <- as.data.frame(model@model$variable_importances)
# load lime explainer--------
explainer <- readRDS("explainer")
```


```{r}
# generate simulated values
test.sim <- reactive(
    data.frame(
      `Chr_GENERAL_Age` = input[["Chr_GENERAL_Age"]],
      `Chr_GENERAL_Sex` = input[["Chr_GENERAL_Sex"]],
      `Chr_GENERAL_Triglyzeride` = input[["Chr_GENERAL_Triglyzeride"]],
      `Chr_GENERAL_Natrium` = input[["Chr_GENERAL_Natrium"]],
      `Chr_GENERAL_GPT_ALT` = input[["Chr_GENERAL_GPT_ALT"]],
      `Chr_GENERAL_Erythrozyten` = input[["Chr_GENERAL_Erythrozyten"]],
      `Chr_GENERAL_Kalium` = input[["Chr_GENERAL_Kalium"]],
      `Chr_GENERAL_TSH` = input[["Chr_GENERAL_TSH"]],
      `Chr_GENERAL_Eiwei_Egesamt` = input[["Chr_GENERAL_Eiwei_Egesamt"]],
      `Chr_GENERAL_Leukozyten` = input[["Chr_GENERAL_Leukozyten"]],
      check.names = FALSE) %>%
      mutate_if(is.character, as.factor)
)

# get SHAP_values
SHAP_values <- reactive(
  {
    predict_contributions.H2OModel(model, as.h2o(test.sim()))
  }
)
# shap dataframe
shap_df <- reactive(
  {
    SHAP_values() %>%
      as.data.frame(check.names = FALSE) %>%
      select(-BiasTerm) %>%
      gather(feature, shap_value) %>%
      group_by(feature) %>%
      mutate(shap_importance = mean(abs(shap_value)),
             shap_force = mean(shap_value)) %>% 
      ungroup() %>%
      filter(feature %in% loess.Table$variable) %>%
      mutate(feature =  gsub("Chr_", "",feature)) 
      
  }
)
# get prediction
Prediction <- reactive(
  h2o.predict(model, as.h2o(test.sim())) %>%
    as.data.frame()
)

# get probability
Probability <- reactive(
  h2o.predict(model, as.h2o(test.sim())) %>%
    as.data.frame()
)

# get odds

odds <- reactive(
  Probability()$microlithiasis/(1- Probability()$microlithiasis)
)

# get confidence
Confidence <- reactive(
  if (Prediction() == 1) {
    -log(Probability()$microlithiasis)
  } else {
    -log(1-Probability()$microlithiasis)
  }
  
)

# get lime explanation
explanation <- reactive(
  explain(test.sim(), 
         explainer, 
          n_labels  = 1, 
          n_features = 14,
          n_permutations =10000)
)

```

Sidebar {.sidebar}
======================================================================
Values at the Baseline

### Patients characteristics
```{r}
numericInput(inputId = "Chr_GENERAL_Age",
            label = "Age",
            50)
selectInput(inputId = "Chr_GENERAL_Sex", 
            label = "Gender",
            list("Male" = "M", "Female" = "F"))
```

### Complete Blood Count
```{r}
selectInput(inputId = "Chr_GENERAL_Erythrozyten", 
            label = "RBC count",
            list( "4.54 - 5.77 T/l(Male), 3.96 - 5.16T/l (Female)" = "WL",
                  "< 4.54T/l(Male), < 3.96T/l (Female)" = "LLN",
                  "> 5.77T/l(Male), > 5.16T/l (Female)" = "ULN",
                  "Unknown" = NA))
selectInput(inputId = "Chr_GENERAL_Leukozyten", 
            label = "WBC count",
            list( "3.9 - 9.8G/l (Female), 4 - 10.4G/l (Female)" = "WL",
                  "< 3.9G/l(Male), < 4G/l (Female)" = "LLN",
                  "> 9.8G/l(Male), > 10.4T/l (Female)" = "ULN",
                  "Unknown" = NA))
```

### Clinical lab measurement
```{r}
selectInput(inputId = "Chr_GENERAL_Triglyzeride", 
            label = "Triglycerides",
            list( "0 - 150 mmol/L" = "WL",
                  "> 150 mmol/L" = "ULN",
                  "Unknown" = NA))

selectInput(inputId = "Chr_GENERAL_Natrium", 
            label = "Sodium",
            list( "135 - 145 mmol/L" = "WL",
                  "< 135 mmol/L" = "LLN",
                  "> 145 mmol/L" = "ULN",
                  "Unknown" = NA))

selectInput(inputId = "Chr_GENERAL_GPT_ALT", 
            label = "GPT/ALT",
            list( "0 - 34 U/L (Female), 0 - 49 U/L (Male)" = "WL",
                  "> 34 U/L (Female), > 49 U/L (Male)" = "ULN",
                  "Unknown" = NA))

selectInput(inputId = "Chr_GENERAL_Kalium", 
            label = "Potassium",
            list( "3.5 - 5.1 mmol/L" = "WL",
                  "< 3.5 mmol/L" = "LLN",
                  "> 5.1 mmol/L" = "ULN",
                  "Unknown" = NA))

selectInput(inputId = "Chr_GENERAL_TSH", 
            label = "TSH",
            list( "0.27 - 0.42 mU/L" = "WL",
                  "< 0.27 mU/L" = "LLN",
                  "> 0.42 mU/L" = "ULN",
                  "Unknown" = NA))

selectInput(inputId = "Chr_GENERAL_Eiwei_Egesamt", 
            label = "Total Proteins",
            list( "4 - 7.6 g/dL" = "WL",
                  "< 4 g/dL" = "LLN",
                  "> 17.6 g/dL" = "ULN",
                  "Unknown" = NA))

actionButton("run", "Run Model")
```


Predictor {data-icon="fa-signal"}
======================================================================
Row
-----------------------------------------------------------------------

### odds ratio for Microlithiasis

```{r}
renderValueBox(
  valueBox(round(odds(),1),
           color = ifelse(odds() <1, "green", "red"))
)
```

<!-- ### Probability of Uncomplicated Phase -->

<!-- ```{r} -->
<!-- renderValueBox( -->
<!--   valueBox(paste0(round(Probability.leoss()$p0,5) * 100, "%"), -->
<!--            color= ifelse(Probability.leoss()$p0 < 0.25, "red", -->
<!--                          ifelse(Probability.leoss()$p0 >= 0.25 & Probability.leoss()$p0 < 0.5, "orange", -->
<!--                                 ifelse(Probability.leoss()$p0 >= 0.5 & Probability.leoss()$p0 < 0.65, "dodgerblue", "green"))) -->
<!--   ) -->
<!-- ) -->
<!-- ``` -->


### Probability of Microlithiasis

```{r}
renderValueBox(
  valueBox(paste0(round(Probability()$microlithiasis,2) * 100, "%"),
           color= ifelse(Probability()$microlithiasis < 0.25, "green",
                         ifelse(Probability()$microlithiasis >= 0.25 & Probability()$microlithiasis < 0.5, "dodgerblue",
                                ifelse(Probability()$microlithiasis >= 0.5 & Probability()$microlithiasis < 0.65, "orange", "red")))
  )
)
```

<!-- ### Logloss -->

<!-- ```{r} -->
<!-- renderValueBox( -->
<!--   valueBox(round(Confidence.leoss(),5), -->
<!--            color = ifelse(Confidence.leoss() <0.69, "green", "red"), -->
<!--            icon = ifelse(Confidence.leoss() <0.69, "fa-thumbs-o-up", -->
<!--                          "fa-frown-o")) -->
<!-- ) -->
<!-- ``` -->

<!-- ### Comments -->

<!-- ```{r} -->
<!-- renderValueBox( -->
<!--   valueBox(ifelse(Prediction.leoss()$predict==1 & Probability.leoss()$p0 > 0.5 |  -->
<!--                     Prediction.leoss()$predict==0 & Probability.leoss()$p1 > 0.5, "misclassification of patients", -->
<!--                   "true classification of patients"), -->
<!--            color = "dodgerblue", -->
<!--            icon = ifelse(Prediction.leoss()$predict==1 & Probability.leoss()$p0 > 0.5 |  -->
<!--                            Prediction.leoss()$predict==0 & Probability.leoss()$p1 > 0.5, "fa-hospital-o", -->
<!--                          "fa-ambulance")) -->
<!-- ) -->
<!-- ``` -->

### Predictor recommendation

```{r}
renderValueBox(
  valueBox(ifelse(Prediction()$predict=="other", "others causes of Pancreatitis",
                  "Microlithiasis"),
           color = ifelse(Prediction()$predict=="other", "green", "red")
  )
)
```


Row
-----------------------------------------------------------------------
<font size="5">**"Important notice: For scientific use only. This is not a medical product."**</font>


Row
-----------------------------------------------------------------------
# Explanation {data-icon="fa fa-line-chart"}

```{r}
renderPlot (
  {
    p2 <- plot_features(explanation()) +
      ggtitle("Explanation") +
      scale_fill_manual(values = c("green4", "firebrick")) +
      ggplot_theme
    
    print(p2)
  }
)
```

# Variable importance {data-icon="fa fa-pie-chart"}

```{r}
renderPlot(
  {
    p <- shap_df() %>% 
      select(feature, shap_importance) %>%
      distinct() %>% 
      ggplot(aes(x = reorder(feature, shap_importance), y = shap_importance, fill = shap_importance)) +
      geom_col() +
      coord_flip() +
      xlab(NULL) +
      ylab("mean(|SHAP value|)") +
      ggtitle("Impact on output magnitude") +
      scale_fill_gradient(low = "firebrick1", high = "green4") +
      labs(fill="SHAP importance") +
      ggplot_theme
    
    print(p)
  }
)
```

# Variables force-plot {data-icon="fa fa-arrows-h"}

```{r}

renderPlot (
  { 
    p1 <- shap_df() %>% 
      select(feature, shap_importance, shap_force) %>%
      distinct() %>% 
      mutate(color = ifelse(shap_force < 0, 'Negative', 'Positive')) %>% 
      ggplot(aes(x = reorder(feature, shap_importance), y = shap_force, fill = color)) +
      geom_col() +
      scale_fill_manual("SHAP force", values = c("Negative" = "firebrick", "Positive" = "green4")) + 
      coord_flip() +
      xlab(NULL) +
      ylab("mean(|SHAP value|)") +
      ggtitle("Direction of impact on output magnitude") +
      ggplot_theme 
    
    print(p1)
  }
)
```
